Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-11-26 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
adding anoher test set

\section{Evaluation Results}
\label{sec:eval}
We use a subset of Taillard's benchmark suite \cite{taillard1993benchmarks}, comprising $10$ randomly generated JSP instances 
with $50$ jobs, $15$ machines, and $50\times 15=750$ operations each that are
known to be particularly hard for greedy and stochastic optimization techniques, for the empirical evaluation of our approach.
%Many researchers have studied these instances and presented different approaches to solving them. We also developed different decomposition strategies to solve those. Therefore, it will be possible to measure the success/failure of our proposed model by comparing the results of the strategies developed in the past with those obtained from the proposed algorithm. 
For each instance, we extracted the $12$ features described in Section~\ref{sec:features}. In order to assess their impact % of the features
on the clustering and, consequently, the quality of schedules, we make fix use of the features \stfifo, \stmtwr, and \stest, which provide the starting times of operations obtained by
heuristic greedy search methods, as these three features promised to be informative
in preliminary experiments.
In contrast to that, considering the position of operations in jobs (\textit{OP}),
processing times (\textit{PT}), and jobs' time length (\textit{TLJ})
turned out to be counterproductive in our preliminary investigation,
so that we disregard such features in the following.
The six leftover features, i.e., remaining processing time (\textit{RPT}),
earliest starting time (\textit{EST}), machine load (\textit{ML})
as well as the waiting times \wtfifo, \wtmtwr, and \wtest
based on schedules computed by corresponding greedy algorithms,
are added and combined to feature sets as follows:
\todo{The feature set
\textit{\{ \stfifo, \stmtwr, \stest, RPT, EST, ML \}} would be logical as \textbf{F8},
but it's missing.}
% we store and present the output of the feature selection step and results of the decomposition-based solving using the Answer Set Programming model developed in \cite{el2020job}.
% The feature selection algorithm was initialized with a simple combination that consists of $3$ features: \stfifo, \stmtwr, and \stest. The combinations of the selected features presented below. We neglected the rank of an operation and the time length of a job because they had negative impact results from the preliminary experiments.

\begin{enumerate}[label=]
\fontsize{9pt}{10pt}
\item \textbf{F1}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest \}}
\item \textbf{F2}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT \}}
\item \textbf{F3}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, EST \}} 
\item \textbf{F4}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, ML \}} 
\item \textbf{F5}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, EST \}}
\item \textbf{F6}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, ML \}} 
\item \textbf{F7}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, EST, ML \}} 
\item \textbf{F8}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest \}} 
\item \textbf{F9}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT \}} 
\item \textbf{F10} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST \}} 
\item \textbf{F11} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, ML \}}
\item \textbf{F12} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST \}}
\item \textbf{F13} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, ML \}}
\item \textbf{F14} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST, ML \}}
\item \textbf{F15} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST, ML \}}
\end{enumerate}

\begin{table}[bt]
  \begin{center}
    \caption{Solution quality comparison for different sets of features.}
    \label{tab4}
    \addtolength{\tabcolsep}{1pt}
    \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|} \hline
%      & \multicolumn{11}{|c|}{\textbf{Instances}} \\ \cline{2-12}
      \textbf{Approach}   & TA51                           & TA52                           & TA53                           & TA54 & TA55                           & TA56                           & TA57                           & TA58 & TA59                           & TA60 & AVG  \\ \hline\hline
      \textbf{FIFO}        & 3549                           & 3339                           & \textbf{3160}              & \textbf{3218} & 3291               & 3325                           & 3654                           & \textbf{3299} & \textbf{3344}                           & \textbf{3129} & \textbf{3331} \\
      \textbf{MTWR}        & \textbf{3364}           & \textbf{3304}              & 3168                           & 3494 & \textbf{3237}                           & \textbf{3287}               & \textbf{3633}              & 3591 & 3394                           & 3257 & 3373 \\
      \textbf{Single-shot} & 3632                           & 3615                           & 3481                           & 3462 & 3552                           & 3610                           & 3778                           & 3718 & 3613                           & 3550 & 3601 \\ % \hline
%      \textbf{EST}         
      \textbf{Multi-shot}         & 3506                           & 3773                           & 3478                           & 3497 & 3482                           & 3605                           & 3753                           & 3731 & 3398                           & 3247 & 3547 \\ \hline
      \textbf{F1}          & 3506                           & 3277                           & 3382                           & 3414 & 3308                           & 3353                           & 3605                           & 3352 & 3453                           & 3483 & 3413 \\
      \textbf{F2}          & 3362                           & 3318                           & 3585                           & 3425 & 3441                           & 3380                           & 3573                           & 3412 & 3416                           & \textbf{3315} & 3423 \\
      \textbf{F3}          & 3324                           & 3330                           & 3347                           & 3425 & 3424                           & 3548                           & 3601                           & 3370 & 3301                           & 3617 & 3429 \\
      \textbf{F4}          & 3360                           & 3286                           & 3543                           & 3503 & 3319                           & 3270                           & 3583                           & 3509 & 3339                           & 3563 & 3428 \\
      \textbf{F5}          & 3346                           & 3243                           & 3517                           & 3397 & 3355                           & 3383                           & 3650                           & 3707 & 3508                           & 3591 & 3470 \\
      \textbf{F6}          & \textbf{3294} & 3275                           & 3250                           & 3265 & 3386                           & 3366                           & \textbf{3480} & \textbf{3324} & 3430                           & 3327 & \textbf{3340} \\
      \textbf{F7}          & 3328                           & 3226                           & 3338                           & 3353 & 3301                           & 3564                           & 3592                           & 3496 & 3352                           & 3399 & 3395 \\
      \textbf{F8}          & 3588                           & 3397                           & 3251                           & 3563 & 3498                           & \textbf{3229} & 3621                           & 3517 & 3258                           & 3374 & 3430 \\
      \textbf{F9}          & 3588                           & 3373                           & 3522                           & 3443 & 3385                           & 3306                           & 3543                           & 3716 & 3381                           & 3526 & 3475 \\
      \textbf{F10}         & 3568                           & 3533                           & 3373                           & 3386 & 3530                           & 3362                           & 3608                           & 3644 & 3402                           & 3637 & 3504 \\
      \textbf{F11}         & 3514                           & 3256                           & 3585                           & 3352 & 3365                           & 3344                           & 3670                           & 3611 & \textbf{3145} & 3425 & 3427 \\
      \textbf{F12}         & 3682                           & 3494                           & \textbf{3143} & 3270 & 3309                           & 3332                           & 3632                           & 3471 & 3250                           & 3676 & 3426 \\
      \textbf{F13}         & 3624                           & 3505                           & 3427                           & 3236 & 3370                           & 3338                           & 3749                           & 3437 & 3253                           & 3659 & 3460 \\
      \textbf{F14}         & 3554                           & 3373                           & 3524                           & \textbf{3232} & 3385                           & 3483                           & 3573                           & 3365 & 3284                           & 3767 & 3454 \\
      \textbf{F15}         & 3509                           & \textbf{3184} & 3380                           & 3289 & \textbf{3218} & 3389                           & \textbf{3480} & 3481 & 3290                           & 3569 & 3379 \\ % \hline
      \textbf{Virtual Best} & \textbf{3294}                           & \textbf{3184} & \textbf{3143}                           & \textbf{3232} & \textbf{3218} & \textbf{3229}                           & \textbf{3480} & \textbf{3324} & \textbf{3145}                           & \textbf{3315} & \textbf{3256} \\
\hline
      \end{tabular}
  \end{center}
\end{table}

We utilized the above feature sets for partitioning the operations of JSP instances into
\todo{Please insert number of time windows.}$X$ clusters or time windows, respectively,
and then ran the multi-shot optimization approach introduced in~\cite{el2020job} for
$10$ minutes in total, i.e., \todo{Please insert minutes per time windows.}$X$ minutes per time window,
on an
\todo{Please check and update the machine and operating system setup.}
Intel\textsuperscript{\textregistered} Xeon\textsuperscript{\textregistered} E5520 machine under Linux (Ubuntu 18.04.3).
The resulting quality of schedules in terms of the achieved makespan for each instance is reported in Table~\ref{tab4},
where the first four rows include the greedy FIFO and MTWR search methods supplied by the environment in~\cite{tagesc21a}
as well as single-shot and multi-shot pure ASP optimization, the latter taking earliest starting times instead of 
clustering for the decomposition into \todo{Please insert number of time windows.}$X$ time windows,
for reference.
Among these reference methods, FIFO and MTWR are on par, with a slight advantage of FIFO indicated
by the average given in the last column, while combinatorial optimization by neither single- nor multi-shot ASP 
solving is able to keep step and leads to greater makespans within the time limit for all instances.

Among our feature sets for clustering, in preparation of multi-shot optimization by ASP,
we do not identify any clear winner dominating over all instances.
However, the feature sets \textbf{F6}, \textbf{F8}, \textbf{F11}, \textbf{F12}, and \textbf{F15}
yield significant makespan improvements relative to the other alternatives on particular instances.
This means that considering the features \textit{RPT}, \textit{EST}, \textit{ML}, or
\wtfifo, \wtmtwr, and \wtest in addition to starting times \stfifo, \stmtwr, and \stest by
greedy algorithms is beneficial, while the particular combination of features achieving best schedules varies.
Moreover, our clustering method for JSP instance decomposition consistently outperforms pure ASP optimization,
and specific feature sets are ahead of the greedy FIFO and MTWR algorithms on seven out of ten instances,
as indicated by the virtual best clustering results in the last row of Table~\ref{tab4}.
We thus conclude that the instance decomposition by clustering can enable iterative constraint optimization
to find better schedules than greedy algorithms in a short amount of time, where alternative feature sets deserve
attention and trying several of them in parallel seems advisable.

>>>>

\section{Evaluation Results}
\label{sec:eval}
We use a subset of Taillard's and Demirkol's benchmark suite \cite{taillard1993benchmarks,demirkol1998benchmarks}, comprising $10$ randomly generated JSP instances 
with $50$ jobs, $15$ machines, and $50\times 15=750$ operations each that are
known to be particularly hard for greedy and stochastic optimization techniques, for the empirical evaluation of our approach.
%Many researchers have studied these instances and presented different approaches to solving them. We also developed different decomposition strategies to solve those. Therefore, it will be possible to measure the success/failure of our proposed model by comparing the results of the strategies developed in the past with those obtained from the proposed algorithm. 
For each instance, we extracted the $12$ features described in Section~\ref{sec:features}. In order to assess their impact % of the features
on the clustering and, consequently, the quality of schedules, we make fix use of the features \stfifo, \stmtwr, and \stest, which provide the starting times of operations obtained by
heuristic greedy search methods, as these three features promised to be informative
in preliminary experiments.
In contrast to that, considering the position of operations in jobs (\textit{OP}),
processing times (\textit{PT}), and jobs' time length (\textit{TLJ})
turned out to be counterproductive in our preliminary investigation,
so that we disregard such features in the following.
The six leftover features, i.e., remaining processing time (\textit{RPT}),
earliest starting time (\textit{EST}), machine load (\textit{ML})
as well as the waiting times \wtfifo, \wtmtwr, and \wtest
based on schedules computed by corresponding greedy algorithms,
are added and combined to feature sets as follows:
%\todo{The feature set
%\textit{\{ \stfifo, \stmtwr, \stest, RPT, EST, ML \}} would be logical as \textbf{F8},
%but it's missing.}
% we store and present the output of the feature selection step and results of the decomposition-based solving using the Answer Set Programming model developed in \cite{el2020job}.
% The feature selection algorithm was initialized with a simple combination that consists of $3$ features: \stfifo, \stmtwr, and \stest. The combinations of the selected features presented below. We neglected the rank of an operation and the time length of a job because they had negative impact results from the preliminary experiments.

\begin{enumerate}[label=]
\fontsize{9pt}{10pt}
\item \textbf{F1}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest \}}
\item \textbf{F2}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT \}}
\item \textbf{F3}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, EST \}} 
\item \textbf{F4}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, ML \}} 
\item \textbf{F5}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, EST \}}
\item \textbf{F6}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, ML \}} 
\item \textbf{F7}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, EST, ML \}}
\item  \textbf{F8}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, RPT, EST, ML \}}
\item \textbf{F9}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest \}} 
\item \textbf{F10}\phantom{\textbf{0}} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT \}} 
\item \textbf{F11} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST \}} 
\item \textbf{F12} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, ML \}}
\item \textbf{F13} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST \}}
\item \textbf{F14} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, ML \}}
\item \textbf{F15} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, EST, ML \}}
\item \textbf{F16} \textrightarrow{} \textit{\{ \stfifo, \stmtwr, \stest, \wtfifo, \wtmtwr, \wtest, RPT, EST, ML \}}
\end{enumerate}

\begin{table}[bt]
  \begin{center}
    \caption{Solution quality comparison for different sets of features (Taillard's instances).}
    \label{tab4}
    \addtolength{\tabcolsep}{1pt}
    \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|c|} \hline
%      & \multicolumn{11}{|c|}{\textbf{Instances}} \\ \cline{2-12}
      \textbf{Approach}   & TA51                           & TA52                           & TA53                           & TA54 & TA55                           & TA56                           & TA57                           & TA58 & TA59                           & TA60 & AVG  \\ \hline\hline
      \textbf{FIFO}        & 3549                           & 3339                           & \textbf{3160}              & \textbf{3218} & 3291               & 3325                           & 3654                           & \textbf{3299} & \textbf{3344}                           & \textbf{3129} & \textbf{3331} \\
      \textbf{MTWR}        & \textbf{3364}           & \textbf{3304}              & 3168                           & 3494 & \textbf{3237}                           & \textbf{3287}               & \textbf{3633}              & 3591 & 3394                           & 3257 & 3373 \\
      \textbf{Single-shot} & 3632                           & 3615                           & 3481                           & 3462 & 3552                           & 3610                           & 3778                           & 3718 & 3613                           & 3550 & 3601 \\ % \hline
%      \textbf{EST}         
      \textbf{Multi-shot}         & 3506                           & 3773                           & 3478                           & 3497 & 3482                           & 3605                           & 3753                           & 3731 & 3398                           & 3247 & 3547 \\ \hline
      \textbf{F1}          & 3506                           & 3277                           & 3382                           & 3414 & 3308                           & 3353                           & 3605                           & 3352 & 3453                           & 3483 & 3413 \\
      \textbf{F2}          & 3362                           & 3318                           & 3585                           & 3425 & 3441                           & 3380                           & 3573                           & 3412 & 3416                           & \textbf{3315} & 3423 \\
      \textbf{F3}          & 3324                           & 3330                           & 3347                           & 3425 & 3424                           & 3548                           & 3601                           & 3370 & 3301                           & 3617 & 3429 \\
      \textbf{F4}          & 3360                           & 3286                           & 3543                           & 3503 & 3319                           & 3270                           & 3583                           & 3509 & 3339                           & 3563 & 3428 \\
      \textbf{F5}          & 3346                           & 3243                           & 3517                           & 3397 & 3355                           & 3383                           & 3650                           & 3707 & 3508                           & 3591 & 3470 \\
      \textbf{F6}          & \textbf{3294} & 3275                           & 3250                           & 3265 & 3386                           & 3366                           & \textbf{3480} & \textbf{3324} & 3430                           & 3327 & \textbf{3340} \\
      \textbf{F7}          & 3328                           & 3226                           & 3338                           & 3353 & 3301                           & 3564                           & 3592                           & 3496 & 3352                           & 3399 & 3395 \\

      \textbf{F8}          & 3330                           & 3273                           & 3277                           & 3492 & 3375                           & 3469                           & 3760                           & 3410 & 3485                           & 3573 & 3444 \\

      \textbf{F9}          & 3588                           & 3397                           & 3251                           & 3563 & 3498                           & \textbf{3229} & 3621                           & 3517 & 3258                           & 3374 & 3430 \\
      \textbf{F10}          & 3588                           & 3373                           & 3522                           & 3443 & 3385                           & 3306                           & 3543                           & 3716 & 3381                           & 3526 & 3475 \\
      \textbf{F11}         & 3568                           & 3533                           & 3373                           & 3386 & 3530                           & 3362                           & 3608                           & 3644 & 3402                           & 3637 & 3504 \\
      \textbf{F12}         & 3514                           & 3256                           & 3585                           & 3352 & 3365                           & 3344                           & 3670                           & 3611 & \textbf{3145} & 3425 & 3427 \\
      \textbf{F13}         & 3682                           & 3494                           & \textbf{3143} & 3270 & 3309                           & 3332                           & 3632                           & 3471 & 3250                           & 3676 & 3426 \\
      \textbf{F14}         & 3624                           & 3505                           & 3427                           & 3236 & 3370                           & 3338                           & 3749                           & 3437 & 3253                           & 3659 & 3460 \\
      \textbf{F15}         & 3554                           & 3373                           & 3524                           & \textbf{3232} & 3385                           & 3483                           & 3573                           & 3365 & 3284                           & 3767 & 3454 \\
      \textbf{F16}         & 3509                           & \textbf{3184} & 3380                           & 3289 & \textbf{3218} & 3389                           & \textbf{3480} & 3481 & 3290                           & 3569 & 3379 \\ % \hline
      \textbf{Virtual Best} & \textbf{3294}                           & \textbf{3184} & \textbf{3143}                           & \textbf{3232} & \textbf{3218} & \textbf{3229}                           & \textbf{3480} & \textbf{3324} & \textbf{3145}                           & \textbf{3315} & \textbf{3256} \\
\hline
      \end{tabular}
  \end{center}
\end{table}

We utilized the above feature sets for partitioning the operations of JSP instances into $3$ clusters or time windows, respectively,
and then ran the multi-shot optimization approach introduced in~\cite{el2020job} for
$10$ minutes in total, i.e., $3.3$ minutes per time window,
on an
%\todo{Please check and update the machine and operating system setup.}
Intel\textsuperscript{\textregistered} Core(TM) i7-8650U CPU\textsuperscript{\textregistered} Dell Latitude 5590 under Windows 10.

The resulting quality of schedules in terms of the achieved makespan for each instance is reported in Table~\ref{tab4} and Table~\ref{tab5},
where the first four rows include the greedy FIFO and MTWR search methods supplied by the environment in~\cite{tagesc21a}
as well as single-shot and multi-shot pure ASP optimization, the latter taking earliest starting times instead of 
clustering for the decomposition into $3$ time windows,
for reference.
\begin{table}[bt]
  \begin{center}
    \caption{Solution quality comparison for different sets of features (Demirkol's instances).}
    \label{tab5}

    \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l|l|} \hline
      & \multicolumn{11}{|c|}{\textbf{Instances}} \\ \cline{2-12}
      \textbf{Approach}  & Dmu31  & Dmu32 & Dmu33 & Dmu34 & Dmu35 & Dmu71 & Dmu72 & Dmu73 & Dmu74 & Dmu75 & AVG  \\ \hline

      \textbf{FIFO}  & \textbf{6817} & \textbf{6318} & \textbf{6029} & \textbf{6395} & \textbf{6409} & 9678 & 10349 & 9617 & 9847 & 9479 & 8094 \\
      \textbf{MTWR}  & 7155 & 6042 & 6819 & 6570 & 6881 & 7764 & 8407 & 8411 & 8321 & 7893 & \textbf{7426} \\
      \textbf{Single-shot} & 10370 & 10214 & 10064 & 10682 & 10203 & 6848 & 28369 & 32954 & 35325 & 6992 & 16202 \\
      \textbf{EST} & 10318  & 9522  & 9785 & 10775 & 10398 & \textbf{6492}  & \textbf{6935} & \textbf{7202} & \textbf{7128}  & \textbf{6243} & 8480 \\ \hline
      \textbf{F1}  & 8488  & 8325  & 7831 & 8356 & 8088 & 8593  & 7188 & 7826 & 6611 & 7662 & 7897 \\
      \textbf{F2}  & 8440  & 8298  & \textbf{7663} & 8479 & 7986 & 6994  & 7606 & 7209 & 6627 & 7069 & 7637 \\
      \textbf{F3}  & 8234  & 8401  & 8037 & 8444 & 7780 & \textbf{6590}  & 7785 & 7302 & 6690 & 7051 & 7631 \\
      \textbf{F4}  & 7991  & 8589  & 7996 & 8471 & 8207 & 8091  & 7834 & 6972 & 6708 & 6859 & 7771 \\
      \textbf{F5}  & 8164  & 8103  & 7835 & 8482 & 7802 & 6807  & 8357 & 7328 & 6774 & 7192 & 7684\\
      \textbf{F6}  & \textbf{7709} & 8265 & 7795 & 8475 & \textbf{7678}  & 6611 & 6708 & 7030 &6569 & 6867 & \textbf{7371} \\
      \textbf{F7}  & 8268  & 8553  & 7892 & 8359 & 8032 & 7603  & 6855 & 7223 & 6609 & 7200 & 7659 \\
      \textbf{F8}  & 8873 & 8879 & 8201 & 9126 & 7982 & 6843 & 7971 & 7106 & 7545 & 6970 & 7950 \\
      \textbf{F9}  & 8500  & 8185  & 8533 & 8772 & 8535 & 6726 & 6518& 7130 & 6592 & 7262 & 7675 \\
      \textbf{F10}  & 8322  & 8119  & 8433 & 8910 & 8233 & 6868 & 6764 & 7183 & 6267 & 7459 & 7656 \\
      \textbf{F11} & 8617  & 8383  & 8614 & 8755 & 7969 & 7587 & \textbf{6512} & \textbf{6762}& 6505 & 7376 & 7708 \\
      \textbf{F12} & 8400  & 8124  & 8043 & \textbf{8185} & 8799 & 7849 & 6618 & 6876 & 6397 & 7746 & 7704 \\
      \textbf{F13} & 8916 & 8343  & 8441 & 8331 & 8153 & 7464 & 6757 & 6994 & 6434 & 6961 & 7679 \\
      \textbf{F14} & 8392  & \textbf{7937} & 7943 & 8375 & 8049 & 7310 & 7703 & 6827 & \textbf{6126} & 6893 & 7555 \\
      \textbf{F15} & 8412  & 8210  & 8117 & 8563 & 9068 & 7853 & 6968 & 6909 & 6350  & 7011 & 7746 \\
      \textbf{F16} & 8184 & 8150 & 8295 & 8721 & 8003 & 6997 & 7156 & 6991 & 6355 & \textbf{6584} & 7544 \\ 
      \textbf{Virtual Best} & \textbf{6817} & \textbf{6318} & \textbf{6029} & \textbf{6395} & \textbf{6409} & \textbf{6492} & \textbf{6512} & \textbf{6762} & \textbf{6126} & \textbf{6243} & \textbf{6410} \\
\hline
      \end{tabular}
  \end{center}
\end{table}

Among these reference methods, FIFO and MTWR are on par, with a slight advantage of FIFO indicated
by the average given in the last column, while combinatorial optimization by neither single- nor multi-shot ASP 
solving is able to keep step and leads to greater makespans within the time limit for all instances.

Among our feature sets for clustering, in preparation of multi-shot optimization by ASP,
we do not identify any clear winner dominating over all instances.
However, the feature sets \textbf{F6}, \textbf{F11}, \textbf{F14}, and \textbf{F16}
yield significant makespan improvements relative to the other alternatives on particular instances.
This means that considering the features \textit{RPT}, \textit{EST}, \textit{ML}, or
\wtfifo, \wtmtwr, and \wtest in addition to starting times \stfifo, \stmtwr, and \stest by
greedy algorithms is beneficial, while the particular combination of features achieving best schedules varies.
Moreover, our clustering method for JSP instance decomposition consistently outperforms pure ASP optimization,
and specific feature sets are ahead of the greedy FIFO and MTWR algorithms on seven out of ten instances,
as indicated by the virtual best clustering results in the last row of Table~\ref{tab4}.
We thus conclude that the instance decomposition by clustering can enable iterative constraint optimization
to find better schedules than greedy algorithms in a short amount of time, where alternative feature sets deserve
attention and trying several of them in parallel seems advisable.
